A new breeding crossover approach for evolutionary algorithms

### 2023-09-21 paper.tex
Functions F1-F20 description update.

    We describe how to interpret the results presented in our Box and Whisker charts for each mathematical function. For these experiments, we choose to test the benchmark functions with ten and thirty dimensions, while there are higher dimensions, these two present enough challenges to the algorithms to compare the search performance in this kind of problem. According to the rules of the CEC 2017 Benchmark, the number of runs must be 51. The results in the table are then the box plot showing the median of the 51 runs. In green color, we show the results of the canonical One Point crossover found in the original version of GAs, on the right side, in blue color we show the results of our current proposal, the Continuous Range crossover. Because the goal is to minimize the functions, the closer the error values are to the zero value, the better. Below, we describe Figure~\ref{fig.experiment_F1-F5}, which includes Functions 1 to 5 (F1 to F5).  In function F1 for the 10-dimension difficulty, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test. On the other hand, we needed to find more evidence for thirty dimensions to determine whether any crossover alternative would be better. In the F2 function, for 10 dimensions, again, our proposed approach outperformed the OPx. Moreover, for function F3 for both dimensions, the statistical test found better results for our proposed CRx strategy. At function F4, only for the 10-dimensional problem, the CRx strategy turned out to be better through the statistical test, while for 30 dimensions, there was not a statistically clear winner. Finally, for F5, the statistical test passed only in 10 dimensions.

    We now describe the results for the next set of functions shown in Figure~\ref{fig.experiment_F6-F10}, including functions F6 through F10.

    \begin{itemize}
        \item In function F6, for the category of 10 dimensions, there needed to be more evidence to determine that any of the proposals were best. For the variety of 30, the OPx alternative surpassed our CRx proposal in the statistical test for the first occasion.
        \item At function F7, for the category of 10 dimensions, once again, the CRx strategy outperforms its alternative through the statistical test. For the 30-dimension type, we found not enough evidence to declare any of them as the best proposal.
        \item At function F8, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
        \item At function F9, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.
        \item At function F10, the opposite of the previous function occurred, where for both dimensions, 10 and 30, the classic OPx strategy obtained better results than our CRx proposal by passing the statistical test in both cases.
    \end{itemize}

    We describe the results shown in Figure~\ref{fig.experiment_F11-F15}, including functions F11 through F15.

    \begin{itemize}
        \item At function F11, only for the 10-dimensional category, the original OPx passed the statistical test compared to our proposed strategy CRx, while for the 30-dimensional type, they obtained similar results.
        \item At function F12, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.

    \end{itemize}

>>>>

    We describe how to interpret the results presented in our Box and Whisker charts for each mathematical function. For these experiments, we choose to test the benchmark functions with ten and thirty dimensions, while there are higher dimensions, these two present enough challenges to the algorithms to compare the search performance in this kind of problem. According to the rules of the CEC 2017 Benchmark, the number of runs must be 51. The results in the table are then the box plot showing the median of the 51 runs. In green color, we show the results of the canonical One Point crossover found in the original version of GAs, on the right side, in blue color we show the results of our current proposal, the Continuous Range crossover. Because the goal is to minimize the functions, the closer the error values are to the zero value, the better. Below, we describe Figure~\ref{fig.experiment_F1-F5}, which includes functions F1 to F5.  In function F1 for the 10-dimension difficulty, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test. On the other hand, we needed to find more evidence for thirty dimensions to determine whether any crossover alternative would be better. In the F2 function, for 10 dimensions, again, our proposed approach outperformed the OPx. Moreover, for function F3 for both dimensions, the statistical test found better results for our proposed CRx strategy. At function F4, only for the 10-dimensional problem, the CRx strategy turned out to be better through the statistical test, while for 30 dimensions, there was not a statistically clear winner. Finally, for F5, the statistical test passed only in 10 dimensions.

    We now describe the results for the next set of functions shown in Figure~\ref{fig.experiment_F6-F10}, including functions F6 through F10. In function F6, only for the 30-dimension difficulty, the canonical OPx alternative surpassed our proposal in the statistical test for the first occasion. On the following function, F7, only for the 10-dimension, our proposed CRx outperforms its alternative through the statistical test. Moreover, for functions F8 and F9 for both dimensions, the statistical test found better results for our proposed CRx strategy. For the function F10, the opposite of the previous function occurred, where for both dimensions, the classic OPx strategy obtained better results than our proposal. We describe the results in Figure~\ref{fig.experiment_F11-F15}, including functions F11 through F15. At function F11, only for the 10-dimension, the original OPx passed the statistical test compared to our proposed strategy. For function F12, the CRx strategy found better results for both tested dimensions than the canonical alternative, passing the statistical test. Our proposed strategy proved a better alternative for the F13, F14, and F15 functions at the 30 dimensions test run. We continue describing the results shown in Figure~\ref{fig.experiment_F16-F20}, which includes functions F16 to F20. At function F16, both alternatives obtained similar results on both tested dimensions. While for function F17 only for the 10-dimension, our proposed strategy proved better. On the other hand, at functions F18 and F19, only at the 30-dimension test, our proposed CRx passed the statistical test. Finally, for function F20, both crossover alternatives tested equivalent results.

    We continue with the description for the following set of functions shown in Figure~\ref{fig.experiment_F21-F25}, which includes functions f21 through F25.

    We finalize with the description for our last set of functions shown in Figure~\ref{fig.experiment_F26-F30}, which includes functions f26 through F30.
